---
title: "Compare County-Level to Covidestim"
author: "Quinn White"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    df_print: paged
    code_folding: hide
    css: ../../css/template.css
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 18, fig.height= 12)

# test 

library(tidyverse)
library(latex2exp)
library(here)
library(scales)
library(viridis)

theme_c <- function(...){ 
   # font <- "Helvetica"   #assign font family up front
    theme_bw() %+replace%    #replace elements we want to change
    
    theme(
      
      
      #text elements
      plot.title = element_text(             #title
                   size = 20,                #set font size
                   face = 'bold',            #bold typeface
                   hjust = .5,
                   vjust = 3),               
      
      plot.subtitle = element_text(          #subtitle
                   size = 14,
                   hjust = .5,
                   face = 'italic',
                   vjust = 3),               #font size
      
      axis.title = element_text(             #axis titles
                   size = 25),               #font size
      
      axis.text.x = element_text(              #axis text
                   size = 18),
      legend.text = element_text(size = 18),
      # t, r, b, l
      plot.margin = unit(c(1,.5,.5,.5), "cm"),
      legend.position = "right",
      strip.text.x = element_text(size = 16, face = "bold", color="white"),
      strip.background = element_rect(fill = "#3E3D3D")
      ) %+replace%
      theme(...)
   
}

```



# Massachusetts

```{r}

state <-  "ma"

priors_versions <- c("v1", "v2", "v3", "v4")


versions <- tibble(
  version = c("v1", "v2", "v3", "v4"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
    "$P(S_1|untested)$ Centered at Emp. Value"),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values"
       
    ) )
)


state_corrected_path <- here("analysis/results/adj_biweekly_county/", state, "/")

################################
# read fips 
################################
fips <- read_tsv(here::here("data/demographic/county_fips.tsv")) %>%
  rename_with(tolower)

fips <- fips %>% 
  mutate(fips =ifelse( name %in% c("Dukes", "Nantucket") & state == "MA", 
                              "25007,25019", fips),
         name = ifelse(name %in% c("Dukes", "Nantucket") & state == "MA",
                              "Nantucket Dukes", name)) %>%
  distinct() %>%
  select(fips,county_name = name)

################################
# ESTIMATED
################################
dates <- readRDS(here("data/date_to_biweek.RDS")) %>%
  group_by(biweek) 

corrected <- map_df(priors_versions, ~readRDS(
        paste0(state_corrected_path, "adj_",
               .x, 
               ".RDS")) %>% 
          mutate(version = .x)) %>%
  left_join(dates, relationship = "many-to-many") %>%
  inner_join(fips)
  

corrected <- corrected %>%
  left_join(versions)

covidestim <- readRDS(here("data/covidestim/covidestim_biweekly_all_counties.RDS")) %>%
  select(-c(date,week)) %>%
  distinct() 


joined <- corrected %>%
  left_join(covidestim, relationship="many-to-many") %>%
  left_join(versions)


# for facet_wrap latex formatting
joined <- joined %>%
   mutate(county_name = paste0("$", county_name, "$"),
         county_name = gsub(" ", "\\,", county_name))  

  
  


```


### Heatmap for Ratio of Estimated to Observed


```{r}

######################################################
# HEATMAP OF RATIO OF ESTIMATED TO OBSERVED
######################################################

heatmap_dat <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(biweek, county_name, exp_cases_median, positive) %>%
  summarize(date = min(date)) %>%
  ungroup() 
  

# group similar states together
wide <- heatmap_dat %>%
    mutate(ratio= exp_cases_median/positive) %>%
  select(-c(exp_cases_median, positive)) %>%
  pivot_wider(names_from=county_name,values_from =ratio)

heatmap_dat %>%
  mutate(county_name = gsub("Nantucket", "Nantucket and", county_name)) %>%
  mutate(ratio=exp_cases_median/positive) %>%
  mutate(date_lab = format(as.POSIXct(date),format="%b %d %Y")) %>%
  group_by(county_name) %>%
  mutate(m = median(ratio)) %>%
  ungroup() %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(county_name,m),
             fill =exp_cases_median/positive)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1) +
  labs(x="",
       y= "County",
       fill = "Ratio of Estimated Cases\nto Observed",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Massachusetts",
       subtitle = TeX("Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(axis.text.x = element_text(size=11, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title = element_text(size=16),
        legend.title = element_text(face="bold", size=18),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20))

# which biweeks are highest?
heatmap_dat %>%
  mutate(ratio=exp_cases_median/positive) %>%
  group_by(biweek) %>%
  summarize(m=median(ratio),
            date=min(date)) %>%
  arrange(desc(m))

ggsave(here('thesis/figure/ma_county_heatmap_ratio_est_observed.pdf'),
       height=10,
       width =13,
       dpi=400)


```

### Ranking Ratio of Estimated to Observed


```{r}

subset <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")

ranks <- subset %>%
  mutate(ratio = exp_cases_median/positive,
         tested = total/population) %>%
  # one observation per biweek per state
  select(biweek, date, ratio, county_name,tested) %>%
  group_by(biweek,ratio,county_name,tested) %>%
  summarize(date=min(date)) %>%
  # rank for each time interval
  group_by(biweek) %>%
  mutate(rank = rank(ratio),
         rank_tested=rank(-tested)) 


ranks %>%
  ungroup() %>%
  ggplot(aes(x=date, y = ratio, color = county_name,
             group=county_name)) +
  geom_point() +
  geom_line()
  


ranks %>%
  ungroup() %>%
  ggplot(aes(x=date, y = rank, color = county_name,
             group=county_name)) +
  geom_point() +
  geom_line()
  



ranks %>%
  ungroup() %>%
  ggplot(aes(x=rank_tested, y = rank, color = county_name,
             group=county_name)) +
  geom_point() 




r <- ranks %>%
  mutate(rank_group = case_when(
    rank <= 3 ~  "Top 3",
    rank > 10 ~ "Bottom 3",
    TRUE ~ "Middle" )) %>%
  group_by(county_name, rank_group) %>%
  mutate(n=n()) %>%
  group_by(county_name) %>%
  mutate(max_group = rank_group[which.max(n)]) %>%
  filter( max(n) >=20) %>%
  filter(max_group != "Middle")  %>%
  ungroup()


end_labs <- r %>%
  ungroup() %>%
  filter(date==max(date)) %>%
  # shift to the right
  mutate(date = date + days(10)) %>%
  select(county_name, rank, date) %>%
  ungroup()

```

```{r}

##############################
# RANK PLOT OVER TIME
##############################
# 
# set.seed(999)
# 
# pal1 <-viridis_pal(option="viridis", end = .9, begin=.3)(3)
# pal2 <- viridis_pal(option="rocket", end = .9, begin=.3)(2)
# pal3 <- viridis_pal(option="magma", end = .9, begin=.3)(2)
# pal4 <- viridis_pal(option="mako", end = .8, begin=.3)(2)
# pal5 <- viridis_pal(option="cividis", end = .9, begin=.1)(3)
# 
# 
# rankpal <- c(pal1, pal2, pal3,pal4,pal5)
# indexes <- sample.int(length(rankpal), replace=FALSE)
# rankpal <- rankpal[indexes]


set.seed(123)

rankpal <- c("#b4ddd4", "#7b2c31", "#65d04b", "#da239b", "#b7d165", "#453fbc", "#658114", "#af3fe8", "#ffb947", "#0a60a8", "#f87945", "#16d0ae")

rankpal <- c("#851657", "#be3acd", "#19a71f", "#824598", "#ed820a", "#BB8E37", "#974810", "#1f84ec", "#d02023", "#059dc5", "#f23387", "#16d0ae")

indexes <- sample.int(length(rankpal), replace=FALSE)
rankpal <- rankpal[indexes]



r %>%
 # filter(rank_group!="Middle") %>%
  ggplot() +
  geom_point(aes(x=date,y=rank, 
             group=county_name,
             color= county_name),
             size=.5) +
  geom_line(aes(x=date,y=rank, 
             group=county_name,
             color= county_name)) +
 # facet_wrap(~max_group) +
  ggrepel::geom_text_repel( aes(x= date-days(4),
                y = rank,
                color=county_name,
                label = county_name),
           end_labs,
           min.segment.length=2,
           nudge_y=0,
           hjust=0,
           size=7,
           direction="y",
           force_pull=9,
           box.padding=.15) +
  theme_c(legend.position="none",
          axis.text.x = element_text(size=17,angle=60)) +
  theme(plot.subtitle =element_text(size=19, margin=margin(4,0,4,0)),
        axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=19)) +
 # scale_color_brewer(palette="Dark2")  +
  scale_color_manual(values=rankpal) +
  scale_x_date(date_breaks="1 months", date_labels = "%b %Y",
               limits = c(ymd("2021-03-01"),
                          ymd("2022-03-05"))) +
  labs(y = "Rank of Ratio",
       title = "Rank of Estimated Infections to Observed Infections Over Time",
       subtitle = "For Counties Ranked in the Top or Bottom 3\nfor More Than 80% of Time Intervals",
       x="") +
  scale_y_reverse(breaks=seq(1,13, by=1))


ggsave(here('thesis/figure/rank-ratio-over-time-ma-county.pdf'), height=8,width=13)

  

subset %>%
  filter(county_name == "Alger") %>%
  ggplot(aes(x= date,y=exp_cases_median)) +
  geom_line()
  

subset %>%
  filter(county_name == "Alger") %>%
  ggplot(aes(x= date,y=exp_cases_median/positive)) +
  geom_line()

```




## Faceted by version


```{r}


pal <- c("#10BAC5", "#1B10C5", "#EFB719", "#900C3F")

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Emp. Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$",
               "$\\beta$ Centered at Emp. Value"
               )

joined %>%
  filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=FALSE) +
   geom_linerange(aes(xmin = xmin,
                      xmax=xmax,
                      y = positive,
                      color = 'obs')) +
  facet_grid(county_name~vlabel, scales = "free_y",
              labeller=as_labeller(
               latex2exp::TeX, default = label_parsed)) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 60, size = 16),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 30,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 10),
          plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 18)) +
  scale_fill_manual(values = pal)  +
  labs(y = "Estimated Cases",
       title = paste0("Estimated Cases by Version in ", toupper(state))) +
  scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))




ggsave(here::here(paste0('thesis/figure/', state, '_pb_compared_to_observed.pdf')), 
       height=21, width = 15, dpi=400)









```

## All versions together 

```{r}

joined %>% 
  group_by(biweek) %>%
 filter(biweek >=6) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date,
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=TRUE) +
   # geom_linerange(aes(xmin = xmin,
   #                    xmax=xmax,
   #                    y = exp_cases_median,
   #                    color =vlabel)) +
  facet_wrap(~county_name, scales = "free_y",
              labeller=as_labeller(
               latex2exp::TeX, default = label_parsed),
             ncol = 3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 30, size = 16),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 32,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 18),
          plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 20,hjust=0)) +
#  scale_color_manual(values = pal, labels =TeX(names(pal)))  +
   scale_fill_manual(values = pal, labels =TeX(names(pal)),
                     name ='') +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Massachusetts"),
       x="") +
  guides(fill = guide_legend(byrow=TRUE,nrow=4))


ggsave(here::here(paste0('thesis/figure/', state, '_pb_compare_versions.pdf')), 
       height=19, width = 18, dpi=400)

```


### Compare Trends in Ratio to Trends in Infections


```{r}


subset <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")

library(cowplot)

plot_county <- function(county) {
  
  subset_county <- subset%>%
  filter(county_name==county)
  
  subset_county %>%
  group_by(biweek) %>%
  mutate(mindate=min(date),
         maxdate=max(date)) %>%
  ggplot() +
  geom_ribbon(aes(x=date,ymin=exp_cases_lb, ymax=exp_cases_ub),
              alpha=.7) +
  geom_linerange(aes(xmin=mindate,xmax=maxdate, 
                     y=(exp_cases_median/positive)*median(subset_county$positive),
                     color = 'Ratio of Estimated Infections to Observed'),
                 linewidth =2) +
  theme_c(legend.position='top') +
  labs(x ='', y='Estimated Infections',
       title=county,) +
  scale_color_manual(values=c('Ratio of Estimated Infections to Observed'='#DA6932'), name='') +
  scale_y_continuous(sec.axis=sec_axis(~./median(subset_county$positive), 
                                       name='Ratio of Estimated Infections\nto Observed Infections')) +
    theme(legend.position="none")

}

set.seed(123)

include <- corrected %>%
    select(county_name,population) %>%
    distinct() %>% 
    arrange(desc(population)) %>% 
  slice_head(n=30) %>%
  pull(county_name) %>%
  unique() %>%
  sample(5)


#plot_county("Washtenaw")


pltlist <- map(unique(corrected$county_name), plot_county)
legend <- get_legend(pltlist[[1]] + theme(legend.position="top"))


title_gg <- ggplot() + 
  labs(title = "Comparing Trends in Ratio of Estimated Infections to Observed\nto Trends in Total Infections") + 
  theme(plot.title=element_text(face="bold", hjust = .5, size = 30, margin =margin(5,0,2,0)))


title_row <- plot_grid(title_gg,legend, nrow=2,rel_heights=c(.6,.4))
grid <- plot_grid(plotlist = pltlist, nrow =2, rel_heights = c(.05,.95))

plot_grid(title_row,grid, rel_heights = c(.05,.95), nrow=2)

ggsave(here('thesis/figure/compare-ratio-to-total-ma.pdf'), height=12,width=12)


```

### Compare to Covidestim



```{r}


joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=FALSE) +
   geom_linerange(aes(xmin = xmin,
                      xmax=xmax,
                      y = infections,
                      color = 'covidestim')) +
  facet_grid(county_name~vlabel, scales = "free_y",
              labeller=as_labeller(
               latex2exp::TeX, default = label_parsed)) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 60, size = 16),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 30,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 10),
          plot.subtitle = ggtext::element_markdown(size = 25,
                                                   margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 19)) +
  scale_fill_manual(values = pal)  +
  labs(y = "Estimated Cases",
       x="",
       title = paste0("Estimated Cases by Version in ", toupper(state))) +
  scale_color_manual(values = c('covidestim' = 'darkblue'), labels = 'Covidestim Estimates',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

ggsave(here::here(paste0('thesis/figure/', state, '_pb_compared_to_covidestim.pdf')), 
       height=15, width = 15, dpi=400)


ggsave(here::here(paste0('presentation/figure/', state, '_pb_compared_to_covidestim.jpeg')), 
       height=19, width = 15, dpi=400)









################################
# figure for presentation
#################################



joined %>%
  filter(grepl("Suffolk|Berkshire|Worcester", county_name)) %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=FALSE) +
   geom_linerange(aes(xmin = xmin,
                      xmax=xmax,
                      y = infections,
                      color = 'covidestim')) +
  facet_grid(county_name~vlabel, scales = "free_y",
              labeller=as_labeller(
               latex2exp::TeX, default = label_parsed)) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 40, size = 11),
          axis.text.y=element_text(size=8),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 20,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 12),
          plot.subtitle = ggtext::element_markdown(size = 25,
                                                   margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 14)) +
  scale_fill_manual(values = pal)  +
  labs(x = "",
       y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in 3 Counties in ", toupper(state))) +
  scale_color_manual(values = c('covidestim' = 'darkblue'), labels = 'Covidestim Estimates',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))

ggsave(here('presentation/figure/ma_pb_compared_to_observed_3_counties.jpeg'), 
       height=10, width = 16.5, dpi=600)



###########################
# JUST SUFFOLK IN WEEK 10
###########################

suffolk_10_vals <- joined %>%
  filter(grepl("Suffolk", county_name))  %>%
  filter(biweek==10 & version=="v1") %>%
  select(exp_cases_lb,exp_cases_ub ) %>%
  distinct()

joined %>%
  filter(grepl("Suffolk", county_name)) %>%
  filter( version=="v1") %>%
  mutate(color = ifelse(biweek ==10, "yes", NA)) %>%
  filter(biweek >= 8 & biweek <=22) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             show.legend=FALSE,
             fill="#AEC3CC",
             alpha=.85) +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill=color),
             alpha = .4,
             show.legend=FALSE) +
  scale_fill_manual(na.value=NA, values=c("red")) +
  geom_linerange(xmin=as_date("2021-05-07"), xmax=as_date("2021-05-20"),
                 y=suffolk_10_vals$exp_cases_lb,
                  color = '#DBC37F',
             linewidth = 1.5,
             alpha=1) +
    geom_linerange(xmin=as_date("2021-05-07"), xmax=as_date("2021-05-20"),
                 y=suffolk_10_vals$exp_cases_ub,
                  color = '#DBC37F',
             linewidth =1.5,
             alpha=1) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 0, size = 5),
          axis.text.y=element_text(size=5),
          axis.title = element_text(size=7),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 20,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 12),
          plot.subtitle = ggtext::element_markdown(size = 25,
                                                   margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 14)) +
  labs(x = "",
       y = "Estimated Infections") 
  
  
  
  
ggsave(here('presentation/figure/suffolk_biweek_10.jpeg'), 
       height=2, width =3, dpi=400)




joined %>%
  filter(grepl("Berkshire", county_name)) %>%
  filter( vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  # mutate(color = ifelse(biweek ==10, "yes", NA)) %>%
  # filter(biweek >= 8 & biweek <=22) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             show.legend=FALSE,
             fill="#386A7E",
             alpha=.85) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 0, size = 14),
          axis.text.y=element_text(size=7),
          axis.title = element_text(size=17),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 20,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 12),
          plot.subtitle = ggtext::element_markdown(size = 25,
                                                   margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 14)) +
  labs(x = "",
       y = "Estimated Infections") 
  
  


ggsave(here('presentation/figure/example_output.jpeg'), 
       height=6, width =10, dpi=400)


  
  

```



### Summarizing Concordance with Covidestim

```{r}



ma_concordance <- joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  select(-date) %>%
  distinct() %>%
  select(exp_cases_lb, exp_cases_ub, county_name, biweek, vlabel, infections) %>%
  mutate(in_interval = case_when(
    exp_cases_lb <= infections & infections <= exp_cases_ub ~ "In Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(in_interval, county_name, vlabel) %>%
  summarize(n_per_county=n()) %>%
  group_by(vlabel, in_interval) %>%
  summarize(n_per_version = sum(n_per_county)) %>%
  group_by(vlabel) %>%
  mutate(total = sum(n_per_version)) %>%
  ungroup() %>%
  mutate(prop=n_per_version/total)





#######################################################################
# CONCORDANCE BY ABOVE, BELOW, WITHIN FOR MOST CONCORDANT VERSION 
#######################################################################
ma_concordance_by_county <- joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  select(-date) %>%
  mutate(county_name = gsub("$", "", county_name, fixed=TRUE)) %>%
  select(exp_cases_lb, exp_cases_ub, county_name, biweek, vlabel, infections) %>%
   distinct() %>%
  mutate(in_interval = case_when(
    exp_cases_lb <= infections & infections <= exp_cases_ub ~ "In Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(in_interval, county_name, vlabel) %>%
  summarize(n_per_county=n()) %>%
  group_by(county_name,vlabel) %>%
  mutate(total = sum(n_per_county),
         prop = n_per_county/total) %>%
  mutate(state="MA")



#########################################################
# CONCORDANCE BY COUNTY (NOT VERSION)
#########################################################
best_by_county <- ma_concordance_by_county %>%
  group_by(county_name) %>%
  filter(in_interval=="In Interval" )%>%
  summarize(vlabel = vlabel[which.max(prop)],
            m = max(prop)) 

ma_concordance_by_county %>%
  inner_join(best_by_county) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = in_interval, y =prop)) + 
  geom_bar(stat="identity",position="dodge") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = "For Implementation with Greatest Concordance") +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))
  
ggsave(here('presentation/figure/covidestim_above_below_by_county_ma.jpeg'),height=7, width=12)

```

```{r}

ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")



##############################################
# stacked bar chart of concordance by county
##############################################
ma_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(county_name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Massachusetts: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))
  
ggsave(here('thesis/figure/covidestim_above_below_by_county_ma.pdf'),height=7, width=12)


```

```{r}



#########################################################
# CONCORDANCE BY COUNTY (MOST CONC. VERSION) 
#########################################################
ma_concordance_by_county  %>%
  filter(in_interval=="In Interval") %>%
  group_by(county_name) %>%
  summarize(max_prop =max(prop),
         type = vlabel[which.max(prop)]) %>%
  ungroup() %>%
  ggplot(aes(y = fct_reorder(county_name, max_prop),
             fill = type,
             x= max_prop)) +
  geom_bar(stat="identity",position="dodge", alpha=.8)+
  scale_fill_manual(values = pal,labels=TeX(names(pal)))  +
  theme_c(legend.position="right",
          legend.text=element_text(hjust=0, size = 15),
          axis.title=element_text(size=16),
          axis.text.x=element_text(size=11),
          axis.text.y = element_text(size=14)) +
  labs(y = "", x="Proportion Containing Covidestim Median",
       fill="") 

ggsave(here('presentation/figure/best_version_by_county_ma.jpeg'), height=8,width=11)



in_interval <- ma_concordance %>%
  filter(in_interval == "In Interval") %>%
  mutate(n_interval = n_per_version) %>%
  select(vlabel, n_interval)

labels <- ma_concordance %>%
  filter(in_interval=="In Interval") %>%
  arrange((prop)) %>%
  pull(vlabel) %>%
  unique() %>%
  as.character()


#########################################################
# CONCORDANCE BY VERSION 
#########################################################
ma_concordance %>%
  left_join(in_interval) %>%
  mutate(in_interval=factor(in_interval, 
                            levels=c( 
                                     "In Interval", 
                                     "Above Interval",
                                     "Below Interval"))) %>%
  ggplot(aes(y =fct_reorder(vlabel,n_interval),
             x = prop, 
             fill=in_interval)) +
  #facet_wrap(~fct_reorder((vlabel),m), ncol=1) +
  geom_bar(stat="identity",position="stack", color="darkgray", linewidth=.2) +
#  viridis::scale_fill_viridis(option="mako", begin=.2, discrete=TRUE) +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  theme(
          plot.subtitle = element_text(size=18, face='italic', margin=margin(4,0,4,0))) +
  scale_y_discrete(labels=unname(TeX(labels))) +
  labs(y ="",
       x="Proportion",
       fill = "Covidestim Median:",
       title = "Where Covidestim Medians Fall\nRelative to Probabilistic Bias Intervals",
       subtitle = "By Version, in Massachusetts") +
  scale_fill_manual(values=c("Below Interval"="#7997D2",
                             "In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79"),
                     breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  guides(fill=guide_legend(byrow=TRUE)) +
  scale_x_continuous(n.breaks = 7, expand=c(0,0),limits=c(-.05,1))

ggsave(here('thesis/figure/summarize-concordance-mass-counties.pdf'), width=16,height=7)

```


```{r}


joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=FALSE) +
   geom_linerange(aes(xmin = xmin,
                      xmax=xmax,
                      y = infections,
                      color = 'covidestim')) +
  facet_grid(county_name~vlabel, scales = "free_y",
              labeller=as_labeller(
               latex2exp::TeX, default = label_parsed)) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 60, size = 16),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 20,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 18),
          plot.subtitle = ggtext::element_markdown(size = 25,
                                                   margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 14)) +
  scale_fill_manual(values = pal)  +
  labs(y = "Estimated Infections",
       x="",
       title = paste0("Estimated Infections by Version in ", toupper(state))) +
  scale_color_manual(values = c('covidestim' = 'darkblue'), labels = 'Covidestim Estimates',
                     name = '') +
  guides(color = guide_legend(override.aes = list(linewidth =2)))




```





```{r}

# hampshire

county_cols <- viridis(length(unique(joined$county_name))- 1, option = "mako")
county_cols <- c("red",county_cols )

names(county_cols ) <- c("$Hampshire$", unique(joined$county_name)[  unique(joined$county_name) != "$Hampshire$"])

joined %>%
  mutate(posrate = positive/total,
         size = ifelse(grepl("Hampshire", county_name),'Hampshire', 'not'))  %>% 
  select(biweek, county_name, posrate,size) %>% 
  distinct() %>% 
  ggplot(aes(x=biweek,y=posrate, color = county_name,
             linewidth=size, alpha = size)) + 
  geom_line() +
  scale_linewidth_manual(values=c('Hampshire'=2, 'not'=.5)) +
  scale_alpha_manual(values = c('Hampshire' = 1, 'not'=.4)) +
  scale_color_manual(values=county_cols, labels = TeX(names(county_cols))) +
  theme_c(legend.position = "right",
          legend.text=element_text(hjust=0),
          legend.title = element_text(size  =16, face="bold"),
          axis.text.x = element_text(size = 9)) +
  guides(linewidth="none",
         alpha = "none",
         color = guide_legend(override.aes = list(linewidth = 2.5))) +
  labs(color = "County Name",
       y = "Positivity Rate",
       x= "Biweek",
       title="Hampshire County Positivity Rate\nCompared to Other Counties in Massachusetts") +
  scale_x_continuous(n.breaks = 7)
  

ggsave(here::here('thesis/figure/hampshire.pdf'), 
       height=8, width = 14, dpi=400)




ggsave(here::here('presentation/figure/hampshire.pdf'), 
       height=8, width = 14, dpi=400)

```



```{r}

joined %>%
  mutate(county_name = gsub("$","", county_name,fixed=TRUE)) %>%
  select(-date) %>% 
  distinct() %>%
  mutate(in_interval = infections <= exp_cases_ub & infections >= exp_cases_lb) %>%
  filter(!is.na(in_interval)) %>%
  group_by(vlabel, in_interval, county_name) %>%
  summarize(n=n()) %>%
  group_by(county_name, vlabel) %>%
  mutate(tot=sum(n),
         prop_contained = n/tot) %>%
 filter(in_interval) %>%
  group_by(county_name) %>%
  mutate(m = max(prop_contained)) %>%
  ggplot(aes(x=fct_reorder(county_name, m, .desc=TRUE),
             y = prop_contained, color = vlabel)) +
  geom_point(size = 2.3) +
  labs(y = "Proportion of Biweeks Containing Covidestim Estimate",
       x = "County",
       title = "Comparing the Proportion of Biweeks\nWhere Probabilistic Bias Interval Contains Covidestim Estimate")+
    scale_color_manual(values = pal, labels =TeX(names(pal)), name ='')  +
  theme_c(axis.text.x = element_text(angle = 15, size = 14),
          legend.position ="right",
          axis.title = element_text(size = 16))

ggsave(here::here(paste0('thesis/figure/', 
                         state, 
                         '_pb_compared_to_covidestim_proportions.pdf')), 
       height=8, width = 15, dpi=400)



# 
# joined %>%
#   mutate(county_name = gsub("$","", county_name,fixed=TRUE)) %>%
#   select(-date) %>% 
#   distinct() %>%
#   mutate(in_interval = infections <= exp_cases_ub & infections >= exp_cases_lb,
#          posrate=positive/population) %>%
#   group_by(county_name) %>%
#   mutate(posrate=mean(posrate)) %>%
#   filter(!is.na(in_interval)) %>%
#   group_by(vlabel, in_interval, county_name, posrate) %>%
#   summarize(n=n()) %>%
#   group_by(county_name, vlabel,posrate) %>%
#   mutate(tot=sum(n),
#          prop_contained = n/tot) %>%
#   ggplot(aes(x=posrate, y =prop_contained, color = vlabel)) +
#   geom_point()

```




## Michigan


```{r load michigan data}

state <- "mi"


state_corrected_path <- here("analysis/results/adj_biweekly_county/", state, "/")

################################
# read fips 
################################
fips <- read_tsv(here::here("data/demographic/county_fips.tsv")) %>%
  rename_with(tolower)

fips <- fips %>% 
  mutate(fips =ifelse( name %in% c("Dukes", "Nantucket") & state == "MA", 
                              "25007,25019", fips),
         name = ifelse(name %in% c("Dukes", "Nantucket") & state == "MA",
                              "Nantucket Dukes", name)) %>%
  distinct() %>%
  select(fips,county_name = name)

################################
# ESTIMATED
################################
dates <- readRDS(here("data/date_to_biweek.RDS")) %>%
  group_by(biweek) 

corrected <- map_df(priors_versions, ~readRDS(
        paste0(state_corrected_path, "adj_",
               .x, 
               ".RDS")) %>% 
          mutate(version = .x)) %>%
  left_join(dates, relationship = "many-to-many") %>%
  inner_join(fips)
  

corrected <- corrected %>%
  left_join(versions)

covidestim <- readRDS(here("data/covidestim/covidestim_biweekly_all_counties.RDS")) %>%
  select(-c(date,week)) %>%
  distinct() 


joined <- corrected %>%
  left_join(covidestim, relationship="many-to-many") %>%
  left_join(versions)


# for facet_wrap latex formatting
# joined <- joined %>%
# #  mutate(county_name = gsub(" ", "~", county_name)) %>%
#    mutate(county_name = paste0('$"', county_name,'"$' ))
          
          # ,
          # county_name= paste0("$ $", county_name))
          # 
          # 
  


```



```{r}

library(scales)


pal <- c("#10BAC5", "#1B10C5", "#EFB719", "#900C3F")

names(pal) <- c(#"$observed$", 
                '$P(S_1|untested)$ Centered at Emp. Value',
                '$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values',
               "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$",
               "$\\beta$ Centered at Emp. Value"
               )

n_counties <- joined$fips %>% unique() %>% length()

size <- ceiling(n_counties/3)

ind <- c(rep(1, size), rep(2, size), rep(3, n_counties - 2*size))

groups <- tibble(group = ind, fips = unique(joined$fips))
# 
# name_f <- function(variable, x) {
#   if (variable == "county_name") {
#     return(as.character(x))
#   }
#   else { 
#     plyr::llply( as.character(x), function(x) parse(x))
#   }
# }

joined %>%
  left_join(groups) %>%
  group_by(group) %>%
  group_split() %>%
  iwalk( ~ { 
    .x %>%
    filter(biweek >=6) %>%
    group_by(biweek) %>%
    mutate(xmin = min(date),
           xmax = max(date)) %>%
    ungroup() %>%
     ggplot() +
    geom_ribbon(aes(x = date, 
               ymin = exp_cases_lb,
               ymax = exp_cases_ub,
               fill = vlabel),
               alpha = .5,
               show.legend=FALSE) +
     geom_linerange(aes(xmin = xmin,
                        xmax=xmax,
                        y = positive,
                        color = 'obs')) +
       facet_grid(county_name ~ vlabel, 
             labeller = labeller(vlabel =as_labeller(TeX, default=label_parsed)),
             scales="free_y") +
    scale_y_continuous(labels = comma) +
    scale_x_date(date_breaks = "2 months", 
                 date_labels = "%b %Y") +
    theme_c(axis.text.x = element_text(angle = 30, size = 16),
            plot.title=element_text(face = "bold",
                                    hjust = .5, 
                                    size = 20,
                                    margin=margin(5,5,15,5,'pt')),
            strip.background = element_rect(fill = "#393939"),
            strip.text = element_text(color =  "white", size = 16),
            strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                        size = 14,
                                        face="bold"),
            strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                         face = "bold",
                                         size = 10),
            axis.text = element_text(size = 8),
            plot.subtitle = ggtext::element_markdown(size = 25,
                                                     margin = margin(3,5,10,5,'pt'),
                                         face = "italic"),
            legend.position = "top",
            legend.text =element_text(size = 14)) +
    scale_fill_manual(values = pal)  +
    labs(y = "Estimated Infections",
         x="",
         title = paste0("Estimated Infections by Version in ", toupper(state))) +
    scale_color_manual(values = c('obs' = 'red'), labels = 'Positive Tests',
                       name = '') +
    guides(color = guide_legend(override.aes = list(linewidth =2)))
  
  
    ggsave(here::here(paste0('thesis/figure/', state, .y, '_pb_compared_to_observed.pdf')),
           height=20, width = 15, dpi=400) }
)


```


```{r}

joined %>% 
  group_by(biweek) %>%
 filter(biweek >=6) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date,
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .5,
             show.legend=TRUE) +
   # geom_linerange(aes(xmin = xmin,
   #                    xmax=xmax,
   #                    y = exp_cases_median,
   #                    color =vlabel)) +
  facet_wrap(~county_name, scales = "free_y",
              labeller=labeller(vlabel =as_labeller(TeX, default=label_parsed)),
             ncol = 3) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x = element_text(angle = 60, size = 16),
          plot.title=element_text(face = "bold",
                                  hjust = .5, 
                                  size = 22,
                                  margin=margin(5,5,15,5,'pt')),
          strip.background = element_rect(fill = "#393939"),
          strip.text = element_text(color =  "white", size = 16),
          strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
                                      size = 14,
                                      face="bold"),
          strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
                                       face = "bold",
                                       size = 10),
          plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
                                       face = "italic"),
          legend.position = "top",
          legend.text =element_text(size = 14)) +
#  scale_color_manual(values = pal, labels =TeX(names(pal)))  +
   scale_fill_manual(values = pal, labels =TeX(names(pal)),
                     name ='') +
  labs(y = "Estimated Infections",x="",
       title = paste0("Estimated Infections by Version in Michigan")) 


ggsave(here::here(paste0('thesis/figure/', state, '_pb_compare_versions.pdf')), 
       height=17, width = 17, dpi=400)

```


```{r}

joined %>%
  mutate(county_name = gsub("$","", county_name,fixed=TRUE),
         county_name = gsub('"', '', county_name, fixed=TRUE)) %>%
  select(-date) %>% 
  distinct() %>%
  mutate(in_interval = infections <= exp_cases_ub & infections >= exp_cases_lb) %>%
  filter(!is.na(in_interval)) %>%
  group_by(vlabel, in_interval, county_name) %>%
  summarize(n=n()) %>%
  group_by(county_name, vlabel) %>%
  mutate(tot=sum(n),
         prop_contained = n/tot) %>%
 filter(in_interval) %>%
  group_by(county_name) %>%
  mutate(m = max(prop_contained)) %>%
  ggplot(aes(x=fct_reorder(county_name, m),
             y = prop_contained, color = vlabel)) +
  geom_point(size = 3.5) +
  labs(y = "Proportion of Two-week Intervals\nContaining Covidestim Estimate",
       x = "County",
       title = "Comparing the Proportion of Two-week Intervals\nWhere Probabilistic Bias Interval Contains Covidestim Estimate")+
    scale_color_manual(values = pal, labels =TeX(names(pal)), name ='')  +
  theme_c(axis.text.x = element_text( size =16, angle =0),
          axis.text.y = element_text(size = 12,hjust=1),
          legend.text = element_text(size = 28, hjust=0),
          axis.title= element_text(size = 25),
          legend.position ="top",
          plot.title = element_text(size = 38, face="bold", margin = margin(2,0,3,0))) +
  scale_y_continuous(n.breaks = 10) +
  guides(color = guide_legend(override.aes = list(size = 8), nrow=4,
                              byrow=TRUE)) +
  coord_flip() 



ggsave(here::here(paste0('thesis/figure/', 
                         state, 
                         '_pb_compared_to_covidestim_proportions.pdf')), 
       height=19, width = 16, dpi=400)

```

### Heatmap

```{r}

######################################################
# HEATMAP OF RATIO OF ESTIMATED TO OBSERVED
######################################################

heatmap_dat <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(biweek, county_name, exp_cases_median, positive) %>%
  summarize(date = min(date)) %>%
  ungroup() 
  

# group similar states together
wide <- heatmap_dat %>%
    mutate(ratio= exp_cases_median/positive) %>%
  select(-c(exp_cases_median, positive)) %>%
  pivot_wider(names_from=county_name,values_from =ratio)

heatmap_dat %>%
  mutate(ratio=exp_cases_median/positive) %>%
  mutate(date_lab = format(as.POSIXct(date),format="%b %d %Y")) %>%
  group_by(county_name) %>%
  mutate(m = median(ratio, na.rm=TRUE)) %>%
  ungroup() %>%
    mutate(ratio=ifelse(ratio>40, 40, ratio)) %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(county_name,m),
             fill =ratio)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1, na.value="white",
                              breaks = c(10,20,30,40), labels = c("10","20","30","40 or greater")) +
  labs(x="",
       y= "County",
       fill = "Ratio of Estimated Cases\nto Observed",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Michigan",
       subtitle = TeX("Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(axis.text.x = element_text(size=15, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title.x = element_text(size=19),
        axis.title.y = element_text(size=19),
        legend.title = element_text(face="bold", size=20, margin=margin(0,0,9,0)),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20))

# which biweeks are highest?
heatmap_dat %>%
  mutate(ratio=exp_cases_median/positive) %>%
  group_by(biweek) %>%
  summarize(m=median(ratio),
            date=min(date)) %>%
  arrange(desc(m))

ggsave(here('thesis/figure/mi_county_heatmap_ratio_est_observed.pdf'),
       height=18,
       width =14,
       dpi=400)


# subset %>%
#   group_by(biweek) %>%
#   mutate(mindate=min(date),
#          maxdate=max(date)) %>%
#   filter(county==Washtenaw) %>%
#   ggplot(aes(xmin=mindate,xmax=maxdate, y=exp_cases_median/population)) +
#   geom_linerange()


```


```{r}


heatmap_dat <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(biweek, county_name, exp_cases_median, positive) %>%
  summarize(date = min(date)) %>%
  ungroup() 

heatmap_dat %>%
  mutate(ratio=exp_cases_median/positive) %>%
  mutate(date_lab = format(as.POSIXct(date),format="%b %d %Y")) %>%
  group_by(county_name) %>%
  mutate(m = median(ratio, na.rm=TRUE)) %>%
  ungroup() %>%
    mutate(ratio=ifelse(ratio>40, 40, ratio)) %>%
  ggplot(aes(x=fct_reorder(date_lab, date),
             y = fct_reorder(county_name,m),
             fill =ratio)) +
  geom_tile() +
 # scale_x_discrete(breaks=breaks_date, labels = breaks_date)  +
  viridis::scale_fill_viridis(option="rocket", direction=-1, na.value="white",
                              breaks = c(10,20,30,40), labels = c("10","20","30","40 or greater")) +
  labs(x="",
       y= "County",
       fill = "Ratio of Estimated Cases\nto Observed",
       title = "Ratio of Median Estimated Infections to Observed Infections\nfor Counties in Michigan",
       subtitle = TeX("Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(axis.text.x = element_text(size=15, angle=90),
        axis.text.y = element_text(size = 17),
        axis.title.x = element_text(size=19),
        axis.title.y = element_text(size=19),
        legend.title = element_text(face="bold", size=20, margin=margin(0,0,9,0)),
        plot.title =element_text(size=22),
        plot.subtitle = element_text(size=20))

```


### Compare Trends in Ratio to Trends in Infections

```{r}


subset <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")

library(cowplot)

plot_county <- function(county) {
  
  subset_county <- subset%>%
  filter(county_name==county)
  
  subset_county %>%
  group_by(biweek) %>%
  mutate(mindate=min(date),
         maxdate=max(date)) %>%
  ggplot() +
  geom_ribbon(aes(x=date,ymin=exp_cases_lb, ymax=exp_cases_ub),
              alpha=.7) +
  geom_linerange(aes(xmin=mindate,xmax=maxdate, 
                     y=(exp_cases_median/positive)*median(subset_county$positive),
                     color = 'Ratio of Estimated Infections to Observed'),
                 linewidth =2) +
  theme_c(legend.position='top') +
  labs(x ='', y='Estimated Infections',
       title=county,) +
  scale_color_manual(values=c('Ratio of Estimated Infections to Observed'='#DA6932'), name='') +
  scale_y_continuous(sec.axis=sec_axis(~./median(subset_county$positive), 
                                       name='Ratio of Estimated Infections\nto Observed Infections')) +
    theme(legend.position="none")

}

set.seed(123)

include <- corrected %>%
    select(county_name,population) %>%
    distinct() %>% 
    arrange(desc(population)) %>% 
  slice_head(n=30) %>%
  pull(county_name) %>%
  unique() %>%
  sample(5)


#plot_county("Washtenaw")


pltlist <- map(c("Washtenaw",include), plot_county)
legend <- get_legend(pltlist[[1]] + theme(legend.position="top"))


title_gg <- ggplot() + 
  labs(title = "Comparing Trends in Ratio of Estimated Infections to Observed\nto Trends in Total Infections") + 
  theme(plot.title=element_text(face="bold", hjust = .5, size = 30, margin =margin(5,0,2,0)))


title_row <- plot_grid(title_gg,legend, nrow=2,rel_heights=c(.6,.4))
grid <- plot_grid(plotlist = pltlist, nrow =2, rel_heights = c(.05,.95))

plot_grid(title_row,grid, rel_heights = c(.05,.95),nrow=2)

ggsave(here('thesis/figure/compare-ratio-to-total-mi.pdf'), height=12,width=12)






```

### Rank Plot

```{r}

subset <- corrected %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value")

subset %>%
  group_by(county_name) %>%
  mutate(x= ifelse( positive == 0, "no_pos", "pos")) %>%
  group_by(county_name, x) %>%
  summarize(n=n()) %>%
  group_by(county_name) %>%
  mutate(tot = sum(n)) %>%
  pivot_wider(names_from=x, values_from=n) %>%
  mutate(across(c(pos,no_pos), ~ifelse(is.na(.x),0,.x))) %>%
  mutate(prop = pos/tot) %>%
  arrange(prop)

ranks <- subset %>%
  mutate(ratio = exp_cases_median/positive,
         tested = total/population) %>%
  # one observation per biweek per state
  select(biweek, date, ratio, county_name,tested) %>%
  group_by(biweek,ratio,county_name,tested) %>%
  summarize(date=min(date)) %>%
  # rank for each time interval
  group_by(biweek) %>%
  mutate(rank = rank(ratio, na.last = "keep"),
         rank_tested=rank(-tested)) %>%
  ungroup()

# 
# ranks %>%
#   ungroup() %>%
#   ggplot(aes(x=date, y = ratio, color = county_name,
#              group=county_name)) +
#   geom_point() +
#   geom_line()
#   
# 
# 
# ranks %>%
#   ungroup() %>%
#   ggplot(aes(x=date, y = rank, color = county_name,
#              group=county_name)) +
#   geom_point() +
#   geom_line()
#   
# 
# 
# 
# ranks %>%
#   ungroup() %>%
#   ggplot(aes(x=rank_tested, y = rank, color = county_name,
#              group=county_name)) +
#   geom_point() 




r <- ranks %>%
  mutate(rank_group = case_when(
    rank <= 15 ~  "Top 15",
    rank >  68 ~ "Bottom 15",
    TRUE ~ "Middle" )) %>%
  group_by(county_name, rank_group) %>%
  mutate(n=n()) %>%
  group_by(county_name) %>%
  mutate(max_group = rank_group[which.max(n)]) %>%
  # 20 or more observations in some group 
  filter( max(n) >=20) %>%
  filter(max_group != "Middle")  %>%
  ungroup()


end_labs <- r %>%
  ungroup() %>%
  filter(date==max(date)) %>%
  # shift to the right
  mutate(date = date + days(10)) %>%
  select(county_name, rank, date) %>%
  ungroup()


##############################
# RANK PLOT OVER TIME
##############################
# 
# set.seed(999)
# 
# pal1 <-viridis_pal(option="viridis", end = .9, begin=.3)(3)
# pal2 <- viridis_pal(option="rocket", end = .9, begin=.3)(2)
# pal3 <- viridis_pal(option="magma", end = .9, begin=.3)(2)
# pal4 <- viridis_pal(option="mako", end = .8, begin=.3)(2)
# pal5 <- viridis_pal(option="cividis", end = .9, begin=.1)(3)
# 
# 
# rankpal <- c(pal1, pal2, pal3,pal4,pal5)
# indexes <- sample.int(length(rankpal), replace=FALSE)
# rankpal <- rankpal[indexes]


set.seed(123)

rankpal <- c("#b4ddd4", "#7b2c31", "#65d04b", "#da239b", "#b7d165", "#453fbc", "#658114", "#af3fe8", "#ffb947", "#0a60a8", "#f87945", "#16d0ae")

rankpal <- c("#851657", "#be3acd", "#19a71f", "#824598", "#ed820a", "#BB8E37", "#974810", "#1f84ec", "#d02023", "#059dc5", "#f23387", "#16d0ae")

indexes <- sample.int(length(rankpal), replace=FALSE)
rankpal <- rankpal[indexes]


# r[which(is.na(r$rank)),]$date <- NA


r_na <- r[which(is.na(r$rank)),]

r %>%
  # filter(!is.na(type)) %>%
  # mutate(type = is.na(rank)) %>%
  # mutate(date = ifelse(is.na(rank), rank,as_date(date, format="%Y %m %d")),
  #        rank_type = is.na(rank)) %>%
 # filter(rank_group!="Middle") %>%
  ggplot() +
  geom_point(aes(x=date,y=rank, 
             color= county_name),
             size=.5) +
  # geom_line(aes(x=date,y=rank, 
  #            group=county_name,
  #            color= county_name)) +
  geom_line(aes(x=date,y=rank,color=county_name)) +
  geom_line(linetype = 2, aes(x=date, y = rank,color=county_name), data = na.omit(r)) +
 # facet_wrap(~max_group) +
  ggrepel::geom_text_repel( aes(x= date-days(4),
                y = rank,
                color=county_name,
                label = county_name),
           end_labs,
           min.segment.length=9,
           nudge_y=0,
           hjust=0,
           size=4,
           direction="y",
           force_pull=9,
           box.padding=.15) +
  theme_c(legend.position="none",
          axis.text.x = element_text(size=17,angle=60)) +
  theme(plot.subtitle =element_text(size=19, margin=margin(4,0,4,0)),
        axis.title.x=element_text(size=16),
        axis.title.y=element_text(size=19)) +
 # scale_color_brewer(palette="Dark2")  +
  scale_color_manual(values=rankpal) +
  scale_x_date(date_breaks="1 months", date_labels = "%b %Y",
               limits = c(ymd("2021-03-01"),
                          ymd("2022-03-15"))) +
  labs(y = "Rank of Ratio",
       title = "Rank of Estimated Infections to Observed Infections Over Time",
       subtitle = "For Counties Ranked in the Top or Bottom 10\nfor More Than 80% of Time Intervals",
       x="") +
  scale_y_reverse(breaks=seq(1,831, by=4))


ggsave(here('thesis/figure/rank-ratio-over-time-mi-county.pdf'), height=8,width=13)

  
corrected %>%
    select(county_name,population) %>%
    distinct() %>% 
    arrange(desc(population))


corrected %>%
    select(county_name,population) %>%
    distinct() %>% 
    arrange((population))


subset %>%
  mutate(pop = ntile(population, 4),
         ratio=exp_cases_median/positive) %>%
  group_by(county_name) %>%
  mutate(pop = min(pop)) %>%
  mutate(pop = case_when(
    pop==1 ~ "Lowest 25%",
    pop ==2 ~ "Second 25%",
    pop==3~ "Third 25%",
    pop==4 ~"Highest 25%"
  ),
  pop=factor(pop, levels=c("Lowest 25%",
                            "Second 25%",
                           "Third 25%",
                           "Highest 25%"))) %>%
  ungroup() %>% 
  group_by(biweek,county_name) %>%
  mutate(date=min(date),
         ratio = unique(ratio)) %>%
  group_by(biweek, pop) %>%
  mutate(m = median(ratio,na.rm=TRUE)) %>%
  ggplot(aes(x=date,y=ratio)) +
  geom_point(alpha =.05,size=.8) +
  geom_point(aes(y=m, color='Median')) +
  facet_wrap(~pop) +
  theme_c() +
  scale_color_manual(values=c('Median'='#e09728')) +
  theme(plot.subtitle=element_text(size=16)) +
  labs(title = "Ratio of Estimated Infections to Observed by Population Size",
       y = "Ratio of Estimated Infections\nto Observed Infections",
       subtitle = "Counties in Michigan",
       x="")

ggsave(here('thesis/figure/mi-ratio-pop.jpeg'), width=14,height=9,dpi=600)



subset %>%
  mutate(pop = ntile(population, 5),
         ratio=exp_cases_median/positive) %>%
  group_by(county_name) %>%
  mutate(pop = min(pop)) %>%
  ungroup() %>% 
  group_by(biweek,county_name) %>%
  mutate(date=min(date),
         ratio = unique(ratio)) %>%
  group_by(biweek, pop) %>%
  mutate(m = median(ratio,na.rm=TRUE)) %>%
  ggplot(aes(x=date,y=m, color=factor(pop))) +
  geom_line()


```





### Summarizing Concordance with Covidestim 


#### By Version


```{r}

mi_concordance <- joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  filter(!grepl("Nantucket", county_name )) %>%
  select(-date) %>%
  distinct() %>%
  select(exp_cases_lb, exp_cases_ub, county_name, biweek, vlabel, infections) %>%
  distinct() %>%
  mutate(in_interval = case_when(
    exp_cases_lb <= infections & infections <= exp_cases_ub ~ "In Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(in_interval, county_name, vlabel) %>%
  summarize(n_per_county=n()) %>%
  group_by(vlabel, in_interval) %>%
  summarize(n_per_version = sum(n_per_county)) %>%
  group_by(vlabel) %>%
  mutate(total = sum(n_per_version)) %>%
  ungroup() %>%
  mutate(prop=n_per_version/total)%>%
  group_by(vlabel) %>%
  mutate(m =prop[which(in_interval=="In Interval")]) %>%
  ungroup()



labels <- mi_concordance %>%
  arrange((m)) %>%
  pull(vlabel) %>%
  unique() %>%
  as.character()

mi_concordance %>%
  mutate(in_interval = factor(in_interval,
                                  levels= c("Above Interval",
                                            "In Interval",
                                             "Below Interval"))) %>%
  ggplot(aes(y =fct_reorder(vlabel,m),
             x = prop, 
             fill=in_interval)) +
  #facet_wrap(~fct_reorder((vlabel),m), ncol=1) +
  geom_bar(stat="identity",
           position="stack",
           color="darkgray", 
           linewidth=.2) +
#  viridis::scale_fill_viridis(option="mako", begin=.2, discrete=TRUE) +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  scale_y_discrete(labels=unname(TeX(labels))) +
  labs(y ="",
       x="Proportion",
       fill = "Covidestim Median:",
       title = "Where Covidestim Medians Fall\nRelative to Probabilistic Bias Intervals",
       subtitle = "By Version, in Michigan") +
  scale_fill_manual(values=c("In Interval" = "#79D2AF", 
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2"),
                    breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  guides(fill=guide_legend(byrow=TRUE)) +
  scale_x_continuous(n.breaks = 7, 
                     expand=c(0,0),
                     limits=c(-.05,1))


ggsave(here(
  'thesis/figure/summarize-concordance-mich-counties.pdf'), width=16,height=7)




```


## By County

```{r, height=8, width=11}


#######################################################################
# CONCORDANCE BY ABOVE, BELOW, WITHIN FOR MOST CONCORDANT VERSION 
#######################################################################
mi_concordance_by_county <- joined %>%
  filter(biweek >=6) %>%
  # covidestim does not report estimates for Nantucket 
  select(-date) %>%
  mutate(county_name = gsub("$", "", county_name, fixed=TRUE)) %>%
  distinct() %>%
  select(exp_cases_lb, exp_cases_ub, county_name, biweek, vlabel, infections) %>%
  mutate(in_interval = case_when(
    exp_cases_lb <= infections & infections <= exp_cases_ub ~ "In Interval",
    exp_cases_lb  > infections  ~ "Below Interval",
    exp_cases_ub < infections ~ "Above Interval"
  ) ) %>%
  group_by(in_interval, county_name, vlabel) %>%
  summarize(n_per_county=n()) %>%
  group_by(county_name,vlabel) %>%
  mutate(total = sum(n_per_county),
         prop = n_per_county/total) %>%
  mutate(state="MI")%>%
  group_by(county_name)



#########################################################
# CONCORDANCE BY COUNTY FOR MOST CONCORDANT VERSION 
#########################################################


# mi_concordance_by_county %>%
#   ggplot(aes(y = fct_reorder(county_name, max_prop),
#              fill = type,
#              x= max_prop)) +
#   geom_bar(stat="identity",position="dodge", alpha=.8)+
#   scale_fill_manual(values = pal,labels=TeX(names(pal)))  +
#   theme_c(legend.position="right",
#           legend.text=element_text(hjust=0, size = 15),
#           axis.title=element_text(size=16),
#           axis.text.x=element_text(size=11),
#           axis.text.y = element_text(size=14)) +
#   labs(y = "", x="Proportion Containing Covidestim Median",
#        fill="")






#########################################################
# CONCORDANCE BY COUNTY (NOT VERSION)
#########################################################
best_by_county <- mi_concordance_by_county %>%
  group_by(county_name) %>%
  filter(in_interval=="In Interval" )%>%
  summarize(vlabel = vlabel[which.max(prop)],
            m=max(prop)) 

mi_concordance_by_county %>%
  inner_join(best_by_county) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = in_interval, y =prop)) + 
  geom_bar(stat="identity",position="dodge") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = "For Implementation with Greatest Concordance")+
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))
  
ggsave(here('presentation/figure/covidestim_above_below_by_county_mi.pdf'), height=8,width=11)



##############################################
# stacked bar chart of concordance by county
##############################################
mi_concordance_by_county %>%
  filter(vlabel=="$P(S_1|untested)$ Centered at Emp. Value") %>%
  group_by(county_name) %>%
  mutate(m = prop[which(in_interval=="In Interval")]) %>%
  ungroup() %>%
  mutate(in_interval = factor(in_interval, levels = c("Above Interval",
                            "In Interval", "Below Interval"))) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = (in_interval), y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Michigan: Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = TeX("For Implementation with $P(S_1|untested)$ Centered at Survey Value")) +
  theme_c() +
  theme(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1))
  
ggsave(here('thesis/figure/covidestim_above_below_by_county_mi.pdf'),height=7, width=12)






mi_concordance_by_county<- mi_concordance_by_county %>%
  mutate(state="MI")


ma_concordance_by_county  <- ma_concordance_by_county %>%
  mutate(state="MA")

# 
# ma_concordance_by_county %>%
#   bind_rows(mi_concordance_by_county) %>%
#   ggplot(aes(x=prop)) +
#   geom_histogram(bins=15) +
#   facet_grid(state~vlabel, scales="free_y")


```

```{r,eval=FALSE}

#########################################################
# CONCORDANCE BY COUNTY (NOT VERSION)
#########################################################
best_by_county <- mi_concordance_by_county %>%
  group_by(county_name) %>%
  filter(in_interval=="In Interval" )%>%
  summarize(vlabel = vlabel[which.max(prop)]) 

mi_concordance_by_county %>%
  inner_join(best_by_county) %>%
  ggplot(aes(x= fct_reorder(county_name,m), 
             fill = in_interval, y =prop)) + 
  geom_bar(stat="identity",position="dodge") +
  theme_c() +
  coord_flip()+
  scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = "For Implementation with Greatest Concordance")+
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 12, hjust=1))
  
ggsave(here('presentation/figure/covidestim_above_below_by_county_mi.pdf'), height=15,width=11)




```

```{r}


#########################################################
# CONCORDANCE BY COUNTY (MOST CONC. VERSION) 
#########################################################
mi_concordance_by_county  %>%
  filter(in_interval=="In Interval") %>%
  group_by(county_name) %>%
  summarize(max_prop =max(prop),
         type = vlabel[which.max(prop)]) %>%
  ungroup() %>%
  ggplot(aes(y = fct_reorder(county_name, max_prop),
             fill = type,
             x= max_prop)) +
  geom_bar(stat="identity",position="dodge", alpha=.8)+
  scale_fill_manual(values = pal,labels=TeX(names(pal)))  +
  theme_c(legend.position="right",
          legend.text=element_text(hjust=0, size = 15),
          axis.title=element_text(size=16),
          axis.text.x=element_text(size=11),
          axis.text.y = element_text(size=14)) +
  labs(y = "", x="Proportion Containing Covidestim Median",
       fill="") 

ggsave(here('presentation/figure/best_version_by_county_mi.pdf'), height=8,width=11)




```



```{r, width=14, height=8}


concordance_both <- mi_concordance %>%
  bind_rows(ma_concordance) %>%
  group_by(vlabel, in_interval) %>%
  summarize(n_per_version_both = sum(n_per_version)) %>%
  group_by(vlabel) %>%
  mutate(total = sum(n_per_version_both)) %>%
  mutate(prop = n_per_version_both/total) %>%
  mutate(m = n_per_version_both[which(in_interval=="In Interval")])  


labels <- concordance_both %>%
  arrange((m)) %>%
  pull(vlabel) %>%
  unique() %>%
  as.character()

concordance_both %>%
  ggplot(aes(y =fct_reorder(vlabel,m),
             x = prop, 
             fill=in_interval)) +
  #facet_wrap(~fct_reorder((vlabel),m), ncol=1) +
  geom_bar(stat="identity",position="dodge", color="darkgray", linewidth=.2) +
#  viridis::scale_fill_viridis(option="mako", begin=.2, discrete=TRUE) +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  scale_y_discrete(labels=unname(TeX(labels))) +
  labs(y ="",
       title = "Proportion of Observations Where Covidestim Medians\nAre Within, Above, or Below Probabilistic Bias Intervals",
       x="Proportion",
       fill = "Covidestim Median:\n") +
  scale_fill_manual(values=c("In Interval" = "#79D2AF", 
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2")) +
  guides(fill=guide_legend(byrow=TRUE)) +
  scale_x_continuous(n.breaks = 7, expand=c(0,0),limits=c(-.05,1))


ggsave(here('presentation/figure/prop_contained.pdf'), width=14, height=8, dpi=400)


```


## By County

```{r}

```







